Gringo 2.0\\--Draft--

### 2008-09-05 doc/documentation/paper.tex
added grounder statistics, don't know where to output them
git-svn-id: https://potassco.svn.sourceforge.net/svnroot/potassco/branches/gringo2@496 3e02f596-3131-0410-8352-e04eeaec37cc

\subsection{Iclingo Options}
Iclingo can be called from the command line via
\begin{verbatim}
 iclingo (iclingo option|file)*
\end{verbatim}
Iclingo is used for incremental solving. For a detailed description see \cite{gekaosscth08a}.
It uses the grounder gringo2.0 and the solver clasp, and therefore all options of gringo2.0, clingo and clasp are valid.
Additionally some options for controlling the incremental behavior are implemented.
\paragraph{\texttt{--incremental,-i}}
Activates the incremental solving. This is the default for iclingo.
\paragraph{\texttt{--istats}}
Prints additional statistics for each incremental step.
\paragraph{\texttt{--imin=<num>}}
At least \texttt{num} incremental steps are solved, whether an answer set has been found or not.
\paragraph{\texttt{--imax=<num>}}
At most \texttt{num} incremental steps are done. After them iclingo stops the search for answer sets.
\paragraph{\texttt{--ibase}}
With this option enabled, iclingo solves only the base program and ignores the cumulative and volatile part of the program.
This option can be helpful when debugging.
\paragraph{\texttt{--istop=<arg>}}
The stop condition during incremental solving can be set.
\begin{itemize}
 \item SAT    : Stop the search process if a solution was found.
 \item UNSAT  : Stop the search process if no solution was found.
\end{itemize}
The default for this option is SAT.
\paragraph{\texttt{--ilearnt=<arg>}}
This option influences the behavior of clasp when used incrementally.
\begin{itemize}
 \item keep   : Learnt nogoods are kept for the next step while solving.
 \item forget : Clasp forgets the learnt nogoods after each incremental step.
\end{itemize}
As default, clasp forgets the learnt nogoods.
\paragraph{\texttt{--iheuristic=<arg>}}
This option sets how to handle heuristic information during incremental solving.
\begin{itemize}
 \item keep   : Heuristic information is kept for the next step while solving.
 \item forget : Clasp forgets the heuristic information after each incremental step.
\end{itemize}
As default, clasp keeps the heuristic information gathered during the previous steps.
\paragraph{Default Parameters}
The default is to read from standard input and search for one model incrementally.
\begin{verbatim}
 iclingo 1 --incremental --istop=SAT --ilearnt=forget 
           --iheuristic=keep --trans-ext=no --eq=5 
           --lookahead=no --lookback=yes --heuristic=Berkmin
           --rand-prop=0.0 --randomize=no --rand-watches=yes
           --restarts=100,1.5 --deletion=3,1.1,3.0
           --minimize=all --contraction=250 --loops=common

>>>>

\subsection{Iclingo Options}
Iclingo can be called from the command line via
\begin{verbatim}
 iclingo (iclingo option|file)*
\end{verbatim}
Iclingo is used for incremental solving. For a detailed description see \cite{gekaosscth08a}.
It uses the grounder gringo2.0 and the solver clasp, and therefore all options of gringo2.0, clingo and clasp are valid.
Additionally some options for controlling the incremental behavior are implemented.
\paragraph{\texttt{--incremental,-i}}
Activates the incremental solving. This is the default for iclingo.
\paragraph{\texttt{--istats}}
Prints additional statistics for each incremental step.
\paragraph{\texttt{--imin=<num>}}
At least \texttt{num} incremental steps are solved, whether an answer set has been found or not.
\paragraph{\texttt{--imax=<num>}}
At most \texttt{num} incremental steps are done. After them iclingo stops the search for answer sets.
\paragraph{\texttt{--iquery=<num>}}
With this option you can set in which step to start with solving the volatile part of the incremental program.
\paragraph{\texttt{--istop=<arg>}}
The stop condition during incremental solving can be set.
\begin{itemize}
 \item SAT    : Stop the search process if a solution was found.
 \item UNSAT  : Stop the search process if no solution was found.
\end{itemize}
The default for this option is SAT.
\paragraph{\texttt{--ilearnt=<arg>}}
This option influences the behavior of clasp when used incrementally.
\begin{itemize}
 \item keep   : Learnt nogoods are kept for the next step while solving.
 \item forget : Clasp forgets the learnt nogoods after each incremental step.
\end{itemize}
As default, clasp forgets the learnt nogoods.
\paragraph{\texttt{--iheuristic=<arg>}}
This option sets how to handle heuristic information during incremental solving.
\begin{itemize}
 \item keep   : Heuristic information is kept for the next step while solving.
 \item forget : Clasp forgets the heuristic information after each incremental step.
\end{itemize}
As default, clasp keeps the heuristic information gathered during the previous steps.
\paragraph{Default Parameters}
The default is to read from standard input and search for one model incrementally.
\begin{verbatim}
 iclingo 1 --incremental --istop=SAT --ilearnt=forget 
           --iheuristic=keep --trans-ext=no --eq=5 
           --lookahead=no --lookback=yes --heuristic=Berkmin
           --rand-prop=0.0 --randomize=no --rand-watches=yes
           --restarts=100,1.5 --deletion=3,1.1,3.0
           --minimize=all --contraction=250 --loops=common
